LSOA domestic Electricty and Gas maps

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Adding age against gas consumption graph

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting gas consumption in the over 65s}
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

>>>>

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting gas consumption in the over 65s}
domgas_LSOA_2019$LSOA11CD <- domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_gas2019 <- merge(domgas_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

dg_age <- dplyr::select(Census_age_gas2019, LSOA11CD, "Local Authority Name",mean_dg2019, "Proportion Over 65", prop_65m)
head(dg_age)
# table(df$`LA Name`)

dg_age$la_name <- dg_age$`Local Authority Name` # make a new variable with an easier name
# select the places we want here
getSolent <- function(df){
  # assumes we are filtering on la_name
  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                           la_name == "East Hampshire"|
                           la_name == "Eastleigh"|
                           la_name == "Fareham"|
                           la_name == "Gosport"|
                           la_name == "Hart"|
                           la_name == "Havant"|
                           la_name == "New Forest"|
                           la_name == "Portsmouth"|
                           la_name == "Rushmoor"|
                           la_name == "Southampton"|
                           la_name == "Test Valley"|
                           la_name == "Winchester"|
                           la_name == "Isle of Wight"
                           )
return(res)
}
Solent_2019g <- getSolent(dg_age) # use our function to get just Solent LAs
nrow(Solent_2019g)
ggplot(Solent_2019g, aes(x= 100 * prop_65m, 
                   y= mean_dg2019, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = " Mean Domestic Gas Consumption (kWh per meter)") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across all LSOAs (2019)")
cor(Solent_2019g$prop_65m, Solent_2019g$mean_dg2019)
```
